---
title: "Final Project"
author: "Tamara Allard"
date: "January 21, 2019"
output: html_document
---



```{r}
library(reshape2)
library(tidyverse)
memdat<-read.csv("Winter2019Rcourse_data.csv", na.strings = "-999")
summary(memdat)

```


1.	I will create a function to calculate d’ that will be used to formulate a d’ Lorsbach variable.

```{r}
d.prime <- function(x1, x2) {
  output <- (scale(x1)) - (scale(x2))
  return(output)
}

memdat$lr_dprime<-d.prime(memdat$lr_hits, memdat$lr_fa)

memdat$lr_dprime
```


2.	I will create 3 additional variables from the hippocampal subfields. These variables will collapse across the lateralization for the head only. Essentially, I will calculate full hippocampal head volumes for CA1, subiculum, and dentate gyrus.

```{r}
col.add <- function(x1, x2) {
  output <- x1 + x2
  return(output)
}

memdat$ca1head<-col.add(memdat$l_ca1head, memdat$r_ca1head)
memdat$dghead<-col.add(memdat$l_dghead, memdat$r_dghead)
memdat$subhead <- col.add(memdat$l_subhead, memdat$r_subhead)

```


3.	I will run three multiple regressions, each will utilize a different hippocampal subfield as the outcome variable. Sex, age, and the d’ variable I create will be predictors. 

```{r}
memlm1<- lm(dghead~sex+age+lr_dprime, data=memdat)
summary(memlm1)

memlm2<- lm(ca1head~sex+age+lr_dprime, data=memdat)
summary(memlm2)

memlm3<- lm(subhead~sex+age+lr_dprime, data=memdat)
summary(memlm3)
```

